\documentclass{article}

% Preamble: Document configuration and packages
\usepackage[utf8]{inputenc} % Input encoding
\usepackage[T1]{fontenc}    % Font encoding
\usepackage[english]{babel} % Language
\usepackage{lipsum}         % Lorem Ipsum placeholder text, remove this line in your actual document

% Document metadata
\title{Hospital Management System Proposal}
\author{Nit Inso Team}
\date{\today}

% Begin the document content
\begin{document}

% Create the title
\maketitle

% Main content
\section{Introduction}
The Hospital Management System aims to provide a comprehensive solution for managing various aspects of hospital operations, including patient appointments, telemedicine, medical records access, analytics, and more.

\section{Key Features}
\subsection{Appointment Scheduling}
\begin{itemize}
    \item \textbf{Anmelden:} Allow patients to register and log in to the system.
    \item \textbf{Terminvereinbarung:} Provide a booking calendar for scheduling appointments, with a focus on usability (Unique Selling Proposition - USP).
    \item \textbf{Auslastung:} Monitor and analyze appointment scheduling to optimize resource utilization.
\end{itemize}

\subsection{Telemedicine}
\begin{itemize}
    \item Provide telemedicine functionalities for remote consultations and patient monitoring (USP).
\end{itemize}

\subsection{Medical Records Access}
\begin{itemize}
    \item Allow patients to access their medical records, including prescriptions from past visits.
\end{itemize}

\subsection{Analytics}
\begin{itemize}
    \item Implement analytics tools to analyze hospital operations and patient data.
\end{itemize}

\subsection{Search}
\begin{itemize}
    \item Implement a search feature to quickly locate patient records, treatments, and other information.
\end{itemize}

\subsection{Treatments}
\begin{itemize}
    \item Manage treatments, including medications and procedures.
\end{itemize}

\subsection{Patient Profiles}
\begin{itemize}
    \item Maintain comprehensive patient profiles with information on medications, allergies, and doctor preferences (though not currently utilized).
\end{itemize}

\subsection{Doctor Profiles}
\begin{itemize}
    \item Manage doctor profiles with capabilities such as prescribing medications, ordering treatments, and patient discharge functions (for patient use).
\end{itemize}

\section{Implementation Plan}
\begin{enumerate}
    \item \textbf{Backend Development:} Utilize Java and the Spring Framework to develop a RESTful API for handling backend functionalities.
    \item \textbf{Frontend Development:} Use Angular to create a dynamic and user-friendly frontend interface for interacting with the system.
    \item \textbf{Integration and Testing:} Integrate the frontend and backend components, and conduct thorough testing with mock data to ensure functionality and reliability.
\end{enumerate}

\section{Conclusion}
The Hospital Management System will streamline hospital operations and improve patient care by providing efficient appointment scheduling, telemedicine capabilities, easy access to medical records, and comprehensive analytics tools.

% End the document content
\end{document}

